$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-18 paper/paper.tex
Allow for structural congruence after reduction
No need to spell out what a congruent equivalence relation is

\begin{nidefinition}
We lift the relation \textsc{StructCong} $\eqeq{}$ and close it under equivalence and congruence in \textsc{Equals} $\eq{}$.
The $\constr{cong-}$* rules define structural congruence under a context $\mathcal{C}[\cdot]$ \cite{Sangio01}, respectively scope restriction, parallel composition, input and output.
The remaining three rules close structural congruence under reflexivity, symmetry and transitivity, respectively. 
\begin{mathpar}
  \datatype
  {P \, Q : \Process_n \\ r : \Rec}
  {P \eq Q : \Set}
  \; \textsc{Equals}

  \inferrule
  {eq : P \eqeq Q}
  {\constr{struct} \; eq : P \eq Q}

  \inferrule
  {eq : P \eq P'}
  {\constr{cong-scope} \; eq : \new P \eq \new P'}

  \inferrule
  {eq : P \eq P'}
  {\constr{cong-comp} \; eq : \comp{P}{Q} \eq \comp{P'}{Q}}

  \inferrule
  {eq : P \eq P'}
  {\constr{cong-recv} \; eq : \recv{x}{}P \eq \recv{x}{}P'}

  \inferrule
  {eq : P \eq P'}
  {\constr{cong-send} \; eq : \send{x}{y}P \eq \send{x}{y}P'}

  \inferrule
  { }
  {\constr{refl} : P \eq P}

  \inferrule
  {eq : P \eq Q}
  {\constr{sym} \; eq : Q \eq P}

  \inferrule
  {eq_1 : P \eq Q \\ \; eq_2 : Q \eq R}
  {\constr{trans} \; eq_1 \; eq_2 : P \eq R}
\end{mathpar}
\end{nidefinition}

@@

  \inferrule
  {eq : P \eq{} P' \\ red : P' \reduce{c} Q}
  {\constr{struct} \; eq \; red : P \reduce{c} Q}
\end{mathpar}

>>>>

\begin{nidefinition}
We lift the relation \textsc{StructCong} $\eqeq{}$ and close it under equivalence and congruence in \textsc{Equals} $\eq{}$.
The relation \textsc{Equals} is structurally congruent under a context $\mathcal{C}[\cdot]$ \cite{Sangio01} and is reflexive, symmetric and transitive. 
\end{nidefinition}

@@

  \inferrule
  {eq_1 : P \eq{} P' \\ red : P' \reduce{c} Q' \\ eq_2 : Q' \eq{} Q}
  {\constr{struct} \; eq \; red : P \reduce{c} Q}
\end{mathpar}
